Text as Policy: \\ Measuring Policy Similarity through Bill Text Reuse

### 2017-02-07 manuscript/ajps/reviews_response.md

 - If we do want to treat policy similarity as an interval-level concept, do we really believe that we can compare blocks of text directly? Some pieces of text are surely more influential than others, and the authors should at least address the issue of text comparability. The discussion of "boilerplate" text addresses this point implicitly, but problems with comparability of text chunks should be made explicit.

[Addressed] This comment is fairly unclear. I don't think it is worth addressing at this point.

Second, in Sections 4-5, parameter setting decisions throughout the paper are not clearly justified. Is there any reason why we might favor a particular gap/mismatch penalization scheme in SWAlign, or the particular search scheme as articulated the last paragraph in Section 4.2? If parameter setting is essentially arbitrary, are there any opportunities for parameter optimization (e.g. cross-validation against some ground-truth objective), or existing values in the literature?

[Addressed] I cited the Burgess et al. paper and said that we were using their parameter values. Frido, it does not look like we are using their values. Please check.

@@

Third, the discussion of TF-IDF weighting to identify boilerplate text is interesting and novel, and I would like to see it expanded further. Other weighting schemes or boilerplate adjustment mechanisms should be discussed (e.g. using word2vec embeddings to classify boilerplate language). The reason for selecting TF-IDF weights in particular should be described in more detail.

[Addressed] I both expanded the discussion of Wilkerson et al. and our approach, and also noted that dealing with boilerplate is an important open area for research in leg politics.

### 2017-02-09 manuscript/ajps/submission/main.tex

We see past work that has identified sets of comparable policies as focusing on sets of policies that meet some threshold of similarity. As such, the latent variable that we argue below is measured effectively through text re-use is {\em policy similarity}. The text in legislation is an aggregate representation of the dimensions underlying the policies proposed therein. These dimensions include the domain of the policy, the ideological position enacted by the policy, the level of specificity in the policy enactment, and several other salient features of policy that are communicated through the text in legislation. We do not claim that the re-use of text can be used to measure these dimensions in a specific, dis-aggregated way. Rather, text re-use serves as a summary measure of the greatest overlap observed across all relevant policy dimensions represented in legislative text. Furthermore, we note that by focusing on legislative text, we are measuring the similarity of the intended policies in terms of how those policies reflect in formal enacting legislation. Once enacted, the policies that are implemented in different states, under different bureaucratic and judicial regimes, will likely differ even if hey are enacted under equivalent legislative language. This divergence in policy implementation is attributable to the inevitable discretion exercised by bureaucratic officials in implementing policy \citep{weingast1983bureaucratic,scott1997assessing,gerber2005state}.

We should emphasize at this point that we are not the first contributors to the legislative politics, or even state legislative politics, literature to use text similarity between bills to measure policy similarity. \citet{wilkerson2015tracing} use text similarity---indeed, the same algorithm we use---to trace the development of very similar policy proposals in legislation produced in the US Congress. \cite{garrett2015} and \cite{burgess2016legislative} both use measures of text similarity in US state legislation to identify bills that incorporate similar forms of model legislation, as provided by legislative/policy advocacy groups. Our contributions to this developing literature are two-fold. First, we broaden the scope of measurement beyond tracing single ideas through bill versions or detecting model legislation---to assessing policy similarity between bills in general. Second, we present multiple validation tests to assess whether our text reuse based measure of policy similarity correlates with benchmarks that we deduce from theories of state policymaking.

@@

In their application of the SW algorithm to the dataset that we use, \citet{burgess2016legislative} optimize the SW algorithm parameters through a predictive experiment. They collected 165 bills that were hand labeled by experts to reuse text from one or more bills within the 165 bill corpus. Looking at all 13,530 pairs of bills that can be formed from the corpus of 165, they used the alignment score to predict whether or not there was text reuse between the bills. They found the optimal parameters, in terms of area under the ROC curve, were a match score of 3, mismatch score of -2, and gap score of -3. We followed \citet{burgess2016legislative} in setting the parameters of the SW algorithm since they use the same data and have already optimized the parameter values. Future work should expand upon treatment of these parameter values in at least two directions. First, it would be valuable to develop a criterion function such that one does not need hand labeled data, which is costly and may exhibit its own biases, to select parameter values. Second, it would be valuable to develop an approach to representing uncertainty in the parameter values as well as in the optimal alignments and scores.

@@

In this approach we follow the common intuition in natural language processing that the informativeness of text is inversely related to the frequency with which that text occurs \citep{robertson2004understanding} (see, e.g., the regular application of term frequency--inverse document frequency (tf-idf) to pre- or post-process text-based datasets and results). Though we cannot speak to whether or not our approach is ultimately better than that taken by \citet{wilkerson2015tracing}, in which they train a classifier to recognize and exclude boilerplate text based on human-labeled data, we note three relative strengths of our approach. First, we do not rely on the development and implementation of a human coding scheme, which is costly and always exhibits some degree of coding error. Second, our approach results in a continuous measure of the information content of text rather than a dichotomous classification of boilerplate or not. Third, and related to the first strength, our approach assigns an informativeness score to all word types, whereas reliance on human classifiers necessarily limits the boilerplate contributions of word types to the word types that were included in the ground truth labeled set.  All this said, dealing with boilerplate/procedural text is an exciting open area of methodological inquiry for quantitative text-as-data research that is focused on legislation.

@@

We use three strategies in order to assess the validity of text reuse as a measure of policy similarity. First, we evaluate whether there is a disproportionately high number of alignments between bills on the same policy area. Second, we analyze how well the bill similarity aggregated to the state level corresponds with policy diffusion networks identified in previous research \citep{desmarais2015}. And third, we study the relationship between the ideological distance between the sponsors of bills and the alignment scores between those bills. If substantive policy content, and importantly, the same ideological direction of the provisions is detected by the alignment algorithm, we will expect an inverse relationship between these two measures. In the validation experiments that follow, we make use of the quantitative, interval level, alignment scores to construct continuous measures of policy similarity. We do this to impose as little information reduction as possible. In the conclusion we discuss the possibility of thresholding these scores in order to classify bill pairs as either containing or not containing matching policy content.

@@

The nature of our measure of policy similarity based on text reuse is that it is high precision and low recall.  As such, in future research we advise scholars to focus on upper quantiles of the distribution of alignments when the inquiry requires the identification of bills that introduce equivalent policies. For predictive modeling, this can be done through the use of quantile regression at high quantiles. For searching out bill pairs, this can be done through thresholding on high alignment scores (e.g., 50+) to indicate the presence of highly similar policy proposals in legislation. Such thresholding may discard informative variation on policy similarity in terms of bill pairs that exhibit borderline overlap when it comes to containing equivalent policy content. On the other hand, high-score thresholding would focus the analysis on bill pairs that reliably contain very similar policy enactments, and pose little risk of a false positive.

@@

%\bibliographystyle{authoryear1} (frido, did you add this? where's the stylefile?)
\bibliographystyle{apsr}
\bibliography{bibliography}

>>>>

We see past work that has identified sets of comparable policies as focusing on sets of policies that meet some threshold of similarity. As such, the latent variable that we argue below is measured effectively through text re-use is {\em policy similarity}. The text in legislation is an aggregate representation of the dimensions underlying the policies proposed therein. These dimensions include the domain of the policy, the ideological position enacted by the policy, the level of specificity in the policy enactment, and several other salient features of policy that are communicated through the text in legislation. We do not claim that the re-use of text can be used to measure these dimensions in a specific, dis-aggregated way. Rather, text re-use serves as a summary measure of the greatest overlap observed across all relevant policy dimensions represented in legislative text. Furthermore, we note that by focusing on legis

@@

@@

In this approach we follow the common intuition in natural language processing that the informativeness of text is inversely related to the frequency with which that text occurs \citep{robertson2004understanding} (see, e.g., the regular application of term frequency--inverse document frequency (tf-idf) to pre- or post-process text-based datasets and results). This measure is different and potentially preferable in two ways. First, it does not require the use of human coders. Second, it places text on a continuum of uniqueness rather than dichotomizes it as boiler plate or not.

@@

We use three strategies in order to assess the validity of text reuse as a measure of policy similarity. First, we evaluate whether there is a disproportionately high number of alignments between bills on the same policy area. Second, we analyze how well the bill similarity aggregated to the state level corresponds with policy diffusion networks identified in previous research \citep{desmarais2015}. And third, we study the relationship between the ideological distance between the sponsors of bills and the alignment scores between those bills. If substantive policy content, and importantly, the same ideological direction of the provisions is detected by the alignment algorithm, we will expect an inverse relationship between these two measures.

@@

The nature of our measure of policy similarity based on text reuse is that it is high precision and low recall.  As such, in future research we advise scholars to focus on upper quantiles of the distribution of alignments when the inquiry requires the identification of bills that introduce equivalent policies. For predictive modeling, this can be done through the use of quantile regression at high quantiles. For searching out bill pairs, this can be done through thresholding on high alignment scores (e.g., 50+) to indicate the presence of highly similar policy proposals in legislation.

@@

\bibliographystyle{authoryear1}
\bibliography{bibliography}
